% resume.tex
% The older version of this resume is stored in Overleaf for rafizsooham@gmail.com

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{-0.0in}

\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}

\setlength{\headheight}{0in}
\setlength{\headsep}{-0.5in}

\setlength{\textheight}{12in}
\setlength{\textheight}{9.5in}

\setlength{\topmargin}{-0.30in}
\setlength{\textwidth}{7in}

\setlength{\topskip}{0in}

\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage{xeCJK}
\setCJKmainfont{Songti SC}  % macOS Song-style font (SimSun equivalent)

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{0pt}}

\newcommand{\resheading}[1]{{\textbf{\Large{#1} \vphantom{p\^{E}}}\vspace{7pt}}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} #2 & \textit{#4} \\
\end{tabular*}\vspace{0pt}}

\newcommand{\resprojectsubheading}[2]{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{0pt}}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{\underline{#3}}}}%
%-----------------------------------------------------------







\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Huge Sooham Rafiz} & \large{+1 (647) 876-6256} \\
        \large{Portfolio: \MYhref{https://www.soohamurai.com}{www.soohamurai.com}}  &  \large{\textbf{rafizsooham@gmail.com}} \\
\end{tabular*}

\vspace{10pt}


\ressubheading{Career Break}{Independent Researcher and Study @ Fudan University}{}{Jul 2025 - Present}
\begin{itemize} \vspace{-\topsep}
\setlength{\parskip}{0pt}
\setlength{\itemsep}{0pt}
\resitem{Took career break following significant investment gains, enabling focus on research interests and extended stay in Shanghai, China studying Chinese and Physics.}
\resitem{Completed performance optimization projects including cache line investigation, CUDA kernel development, and memory hierarchy profiling on Apple M4. \href{https://soohamurai.com/2026/01/31/Measuring-Cache-Hierarchy-on-Apple-M4/}{Blog post on Apple M4 cache hierarchy}}
\resitem{Replicated and extended (Noroozizdeh et al.) paper ``Deep sequence models tend to memorize geometrically; it is unclear why.'' \href{https://github.com/sooham/pathstar-geometric-learning}{Blog post}}
\resitem{Conducted practical research into Pathstar optimization with memmap and sorting techniques. \href{https://soohamurai.com/2025/11/09/practical-memmap-and-sort-on-pathstar/}{Blog post}}
\resitem{Studied Advanced Mechanics and Chinese at Fudan University.}
\resitem{Achieved HSK level 5 proficiency in Chinese. 我在复旦学中文和物理, 都是因为好奇。达到HSK五级水平。}
\end{itemize}
\ressubheading{Short Story (YC'19)}{Senior Software Engineer / ML Engineer}{}{Apr 2024 - Jul 2025}
	\begin{itemize} \vspace{-\topsep}
    \setlength{\parskip}{0pt}
    \setlength{\itemsep}{0pt}
    \resitem{Fine-tuned vision language model cogVLM-17B with LoRA on proprietary data, served via vLLM with Flash Attention 2 for automated fashion cataloging. Achieved F1 score of 0.861 and accuracy of 88\% on evaluation set.}
    \resitem{Designed and deployed ShipmentEngine for tracking 100k+ shipments. Saved 1.8M USD/year in freight costs by engineering platform transition from USPS to Pitney Bowes.}
    \resitem{Built in-house cycle-counting and data ingestion pipelines to eliminate inactive warehouse zones and improve inventory accuracy.}
    \resitem{\textsl{\textbf{Utilized:} PyTorch, DDP, vLLM, Flash Attention, Postgres, AWS, Typescript, Python}}
    \end{itemize}
    \ressubheading{Amazon}{Software Development Engineer II - Payments Team}{}{December 2021 - Nov 2023}
	\begin{itemize} \vspace{-\topsep}
    \setlength{\parskip}{0pt}
    \setlength{\itemsep}{0pt}
    \resitem{Developed real-time Unpaid Time value algorithm and infrastructure for Germany, eliminating batched 3rd party vendor dependency and achieving 1000x speed improvement. Deployed to 2 million warehouse associates.}
    \resitem{Cross-functionally led development of timesheet analysis software serving 1k daily workers in Puerto Rico Amazon Logistic Center.}
    \resitem{\textsl{\textbf{Utilized:} Python, Java, AWS ECS, AWS DDB, Lambda, CloudWatch, Cloudformation, CDK}}
     \end{itemize}
\ressubheading{Qualcomm}{Machine Learning Acceleration Engineer}{}{July 2019 - August 2021}
	\begin{itemize} \vspace{-\topsep}
    \setlength{\parskip}{0pt}
    \setlength{\itemsep}{0pt}
    \resitem{Built a graph compiler to lower computational graphs to ONNX, implementing kernel fusion passes for matmul and batchnorm targeting Qualcomm Adreno GPU and Hexagon DSP.}
    \resitem{Implemented a static quantization library supporting INT8 and INT16 precision with activation-aware quantization for SnapDragon Neural Processor firmware.}
    \resitem{Developed end-to-end CI/CD ML test pipeline and performance dashboard profiling timing, memory footprint, and quantization error across 100+ vision model families (Inceptionv3, MobileNet, YOLO) on multiple hardware targets.}
    \resitem{Reduced memory footprint of compiled binaries for common operators such as Convolution and Argmax.}
    \resitem{\textsl{\textbf{Utilized:} C, Python, PyTorch, ONNX, Qualcomm Hexagon SDK, MLIR}}
    \end{itemize}
    

        \ressubheading{Intel Corporation}{Deep Learning Acceleration Engineer (Intern)}{}{Jun 2018 - Aug 2018}
	\begin{itemize} \vspace{-\topsep}
    \setlength{\parskip}{0pt}
    \setlength{\itemsep}{0pt plus 1pt}
        \resitem{Reduced OpenVINO (a deep learning framework) compile time for CNN models by upto 24 hours using caching optimizations.}
    \resitem{Reduced compile time for building deep convolutional models in regression tests by caching intermediary C object files, libaries and configurations to a Python server, decreasing test time by 16 hours and improving test repeatability.}
    \resitem{Migrated Intel's deep learning framework used by 50+ developers across backwards incompatible updates to development and production environment, sustaining team productivity.}
    \resitem{\textsl{\textbf{Utilized:}  C++, Python, OpenVINO, OpenCL }}
	\end{itemize}


    \ressubheading{Intel Corporation}{FPGA Development Engineer (Intern)}{}{Jun 2017 - May 2018}
	\begin{itemize} \vspace{-\topsep}
    \setlength{\parskip}{0pt}
    \setlength{\itemsep}{0pt plus 1pt}
	%\resitem{Developer for FPGA LDPC codec compatible with 3rd Generation Partnership Project (3GPP) standard of 5G cellular communication.}
	%\resitem{Developed the library for packaging, Quartus synthesis integrations, and user interface for aforementioned LDPC module.}
            \resitem{Created a comprehensive user interface and packaging system using Perl and Tcl, allowing parameter customization, code encryption and code generation. Used in production by multiple customers.}
    \resitem{Built a C++ client and server to query field-programmable gate array (FPGA) registers. This was accomplished by sending Direct Memory Access and Memory Mapped IO requests to FPGA workstations.}
	\resitem{Added FPGA hardware support to Intel's digital signal library by implementing C++ middleware.}
	%\resitem{Improved FPGA IP user documentation through meetings with customers and technical editors.}
	%\resitem{Revised user documentation based on feedback from customers, leading to increased software usability.}
	%\resitem{Programmed an embedded serial command interface and memory peek/poke utilities.}

    \resitem{\textsl{\textbf{Utilized:}  C++, Perl, Tcl, Quartus, Verilog}}
	\end{itemize}

    %\ressubheading{Careerleaf Inc.}{}{Web Developer (Intern)}{Jun 2016 - Sep 2016}
	%\begin{itemize} \vspace{-\topsep}
    %\setlength{\parskip}{0pt}
    %\setlength{\itemsep}{0pt plus 1pt}
	%\resitem{Developed a job management and job listing module using AngularJS and Python backend, satisfying multiple client demands.}
    %\resitem{Reduced redundancy of SQL database by converting schema to Boyce-Codd Normal Form, reducing database size by 80,0000 entries.}
	%\resitem{Worked with a development team using SCRUM software development framework.}
	%\end{itemize}
    %\ressubheading{University of Toronto Aerospace Team}{Toronto, ON}{Avionics Engineer (Club member)}{Sep 2016 - May 2017}
	%\begin{itemize} \vspace{-\topsep}
    %\setlength{\parskip}{0pt}
    %\setlength{\itemsep}{0pt plus 1pt}

	%\resitem{Provided accurate estimation of altitude of rocket nose-cone by implementing a Kalman filter algorithm.}
	%\resitem{Programmed control software to communicate between ground station and the rocket.}
	%\resitem{Helped fellow team-members perform cold-flow and firing tests of the rocket motor.}
    %\resitem{\textsl{\textbf{Utilized:} Arduino, C/C++, LabVIEW}}
	%\end{itemize}

    %\ressubheading{Research Opportunity Program: Game Design }{}{Research Assistant (supervisor: Steve Engels)}{May 2015 - Sep 2015}
	%\begin{itemize} \vspace{-\topsep}
 %\setlength{\parskip}{0pt}
  %  \setlength{\itemsep}{0pt plus 1pt}
   % \resitem{Used C\# and Unity3D to program a multi-level 3D game aimed at teaching tree traversal algorithm BFS and DFS.}
	%\end{itemize}



\resheading{Education}
\ressubheading{University of Toronto}{Honors B.Sc. Computer Science}{}{2014 - 2019}






\resheading{Technologies}
\vspace{2pt}

\textbf{Languages:}  Python, C, C++, CUDA, Java, SQL, Typescript \\
\textbf{ML \& Performance:} PyTorch, DDP/FSDP, ONNX, vLLM, Flash Attention, MLIR \\
\textbf{Tools:} perf, gdb, gprof, valgrind, nvidia-smi, Git \\
\textbf{Hardware:} NVIDIA GPU, Qualcomm Adreno GPU, Hexagon DSP, Intel FPGA \\
\textbf{Infrastructure:} AWS (ECS, Lambda, DDB, EC2, EKS, Cloudformation), Docker

%\resheading{Awards}
%	\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
%		Recognition for Exceptional Performance at Intel Corporation (\$1,000) & 2018 \\
%		CL. Burton Open Scholarship (\$250) & 2015\\
%        Dean's Honours List & 2015 \\
%        3rd Place in CS Pong AI Competition & 2015\\
%        Outstanding Achievement Award for CSC165 & 2015 \\
%        4th Place FIRST Robotics Regionals Shanghai & 2014 \\
%\end{tabular*}

\end{document}

